### 2011-01-26 paper/fitnessEvaluation.tex
Added sentence from other section

@@

We controlled the experiments from a computer that was connected via a wireless Ethernet to the robot. An infrared LED was mounted to the antenna on top of the robot and a Wii remote was attached to the ceiling. The Wii remote tracked the location of the LED. The robot tracked its position via Bluetooth by using the CWiid library\cite{cwiid} to communicate with the Wii remote. If the robot walked outside of the Wii remote’s viewable area, a prompt informed the experimenter. The only human intervention required during an experiment was to move the robot back inside the viewable area and resume the run. This did not interrupt the learning process or result in the loss of data.

>>>>

\edit{Put this in there somewhere:}

To be as fair as possible when obtaining the results presented in
\secref{results}, we picked three random points --- $\vec{\theta}_A$,
$\vec{\theta}_B$, and $\vec{\theta}_C$ --- and started all seven
methods at these points...

@@

We controlled the experiments from a computer that was connected via a
wireless Ethernet to the robot. An infrared LED was mounted to the
antenna on top of the robot and a Wii remote was attached to the
ceiling. The Wii remote tracked the location of the LED. The robot
tracked its position via Bluetooth by using the CWiid
library\cite{cwiid} to communicate with the Wii remote. If the robot
walked outside of the Wii remote's viewable area, a prompt informed
the experimenter. The only human intervention required during an
experiment was to move the robot back inside the viewable area and
resume the run. This did not interrupt the learning process or result
in the loss of data.
